---
title: "Tpcc samsung"
author: "VadimTk"
date: "Jul, 2016"
--output: html_document
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
library(svglite)
library(extrafont)
font_import()
knitr::opts_chunk$set(echo = TRUE,dev="png", 
               dev.args=list(type="cairo-png"),
               dpi=300)
library("RMySQL")
library(stringr)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)

tm<-theme(legend.position="right",
          strip.background = element_rect(colour="red", fill="#CCCCFF"),
          text=element_text(family="Garamond",size=14))

guides(colour = guide_legend(override.aes = list(size=4)))


cons <- dbListConnections(MySQL())
for(con in cons)
    dbDisconnect(con)
con <- dbConnect(MySQL(), user="sbtest", dbname="benchmarks", host="10.20.2.4")

```

# Percona Server/MySQL

## Setup

* Client (tpcc) and server are on the same server. 
* CPU: 56 logical CPU threads servers Intel(R) Xeon(R) CPU E5-2683 v3 @ 2.00GHz
* tpcc 1000 warehouses, 1 schema (about 100GB datasize)
* OS: Ubuntu 16.04 (Xenial Xerus)
* Kernel 4.4.0-28-generic
* Storage devices
  * Samsung SM863 SATA SSD, single device, with ext4 filesystem
  * Samsung 850 PRO SATA SSD, single device, with ext4 filesystem
  * Samsung PM 1725 NVMe SSD, single device

# Results

=============

## cachesize vary

We are varying buffer pool size from 5GB to 115GB. 
With 5GB buffer pool size a very small partion of data fits into memory, this results in intesive foreground IO reads
and intensive background IO writes.

With 115GB almost all data fits into memory, this results in a very small (or almost zero) IO reads, and moderate background IO writes.

All buffer pool sizes in the middle of interval results to corresponding IO reads and writes.

The measurements are taken every 1 sec, so we can see variance in throughput and trends

### Pagesize 16k

The results for innodb_page_size=16k (default), 1 sec resolution
```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "tpcc-mysql 1000W samsung "
p2 = dbGetQuery( con,'SELECT sec, tps, bp, storage 
                 FROM tpcc_results sr 
                 WHERE runsign like "tpcc_1000w_%_16k" and sec>1800
                 ' )


m <- ggplot(p2, aes(x=as.numeric(sec),y=as.numeric(tps),color=storage))

m+geom_point()+expand_limits(y=0)+
  labs(x="BP, GB",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="Storage")+facet_wrap(~bp,labeller = label_both)

```

The average results in NOTPM
```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "tpcc-mysql 1000W samsung, 16k pagesize"
p2 = dbGetQuery( con,'SELECT bp, storage, AVG(tps)*60 tps
                 FROM tpcc_results sr 
                 WHERE runsign like "tpcc_1000w_%_16k" and sec>1800
                 GROUP BY bp,storage
                 ' )


m <- ggplot(p2, aes(x=bp,y=as.numeric(tps),color=storage))

m+geom_point()+geom_line()+expand_limits(y=0)+
  labs(x="BP, GB",y="Throughput, NOTPM",title=title)+tm+scale_color_tableau(name="Storage")+scale_y_continuous(labels = scales::comma)

```

#### Conclusion
Samsung 850 is obviously is not able to keep with with more advanced SM863 and PM1725

PM1725 shows a great benefit with small buffer pool sizes, while in case with big amount of memory, there is practically not difference with SM863.
The reason is that with big buffer pool size MySQL does not push IO subsystem much to use all performance of PM1725

### Pagesize 4k

I also tested how innodb_page_size=4k affects the throughput

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "tpcc-mysql 1000W samsung "
p2 = dbGetQuery( con,'SELECT sec, tps, bp, storage 
                 FROM tpcc_results sr 
                 WHERE runsign like "tpcc_1000w_%_4k" and sec>1800
                 ' )


m <- ggplot(p2, aes(x=as.numeric(sec),y=as.numeric(tps),color=storage))

m+geom_point()+expand_limits(y=0)+
  labs(x="BP, GB",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="Storage")+facet_wrap(~bp,labeller = label_both)


```

The average results in NOTPM
```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "tpcc-mysql 1000W samsung, 4k pagesize "
p2 = dbGetQuery( con,'SELECT bp, storage, AVG(tps)*60 tps
                 FROM tpcc_results sr 
                 WHERE runsign like "tpcc_1000w_%_4k" and sec>1800
                 GROUP BY bp,storage
                 ' )


m <- ggplot(p2, aes(x=bp,y=as.numeric(tps),color=storage))

m+geom_point()+geom_line()+expand_limits(y=0)+
  labs(x="BP, GB",y="Throughput, NOTPM",title=title)+tm+scale_color_tableau(name="Storage")+scale_y_continuous(labels = scales::comma)

```

### Summary
There I show average throughput (in Transactions per Minute)
```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "tpcc-mysql 1000W samsung "
p2avg = dbGetQuery( con,'SELECT  bp, storage,pagesize,avg(tps)*60 tps
                 FROM tpcc_results sr 
                 WHERE runsign like "tpcc_1000w_%" and sec>1800
                 GROUP BY bp, storage,pagesize
                 ' )

m <- ggplot(p2avg, aes(x=as.factor(bp),y=as.numeric(tps),color=pagesize,group=pagesize))
m+geom_point()+geom_line()+expand_limits(y=0)+
  labs(x="BP, GB",y="Throughput, NOTPM",title=title)+tm+scale_color_tableau(name="pagesize")+facet_wrap(~storage,labeller = label_both)


```